---
title: "Data cleaning of SPH publications by gender"
output:
  html_document:
    df_print: paged
---

```{r,include = FALSE}
# read in data with gender variable created in gender_script.R
library(readr)
#install.packages("stringdist")
library(stringdist)
library(dplyr)
library(tidyverse)
library(tidyr)
library(stringr)
```

```{r}
dat_complete <- read_csv("../interim/clean_data_job_title.csv")
```

Checking what needs to be updated:
```{r}
dat_complete %>%
  filter(is.na(author_position) | is.na(individual_position)) %>%
  group_by(author_position, individual_position) %>% 
  summarise(n=n()) 

# 2936 rows with no individual position, 5 of these are alphabetical. Need to backfill
# 2931 rows 
```
Goal: Find missing author positions

```{r}
dat <- dat_complete %>% filter(is.na(author_position))
```

```{r}
dat <- dat %>% mutate(last_name = tolower(last_name),
                      Authors.OR.Authors.Contributors = tolower(dat$Authors.OR.Authors.Contributors))

dat$Name <- gsub("\\([^\\)]+\\)", "", dat$Name)
dat$Name <- gsub("\\.", "", dat$Name)

# Getting initials and ignoring names in brackets
get_initials <- function(name){
  # get first name
  f_name_initials <- unlist(str_split(name, ","))[2]
  
  # remove brackets in name
  f_name_initials_no_bracks <- str_replace(f_name_initials, "\\s*\\([^\\)]+\\)", "")
  
  # get initials
  initials <- paste(unlist(str_extract_all(f_name_initials_no_bracks, "[A-Z]+")), collapse="")

  initials <- tolower(initials)

  return (initials)
}

dat["initials"] <- sapply(dat$Name, get_initials)

```

```{r}
# Checking if the author is contained
dat %>%
  mutate(contained = str_detect(Authors.OR.Authors.Contributors, paste("\\b", last_name, "\\b", sep=""))) %>% 
  group_by(contained) %>%
  summarise(n=n())

  # use a for readability
dat <- dat %>% mutate(a = Authors.OR.Authors.Contributors,
              a = ifelse(ID == 1242860, str_replace(a, "sukriti kc", "kc s"), a),
              a = ifelse(ID == 765517,  str_replace(a, "v. kontis", "kontis v"), a),
              a = ifelse(ID %in% c(1232767, 1236027, 1268038),  str_replace(a, "derqui-fernandez", "derqui"), a),
              a = ifelse(ID == 1236495,  str_replace(a, "fernandez nd", "derqui n"), a),
              a = ifelse(ID %in% c(730067,784991,836293,1245688,1254631),
                     str_replace(a, "basáñez", "basanez"), a),
              a =ifelse(ID == 1102318,
                     str_replace(a, "sophie", "day s"), a),
              a =ifelse(ID == 1211532,
                     str_replace(a, "paul a", "aylin pp"), a),
              a = ifelse(ID == 1267073,
                     str_replace(a, "bórquez a", "borquez a"), a),
              a = ifelse(ID %in% c(701393,1292899,1294145,1314809),
                     str_replace(a, "rönn mm", "ronn mm"), a),
              a = ifelse(ID %in% c(667243,667244,780930,789999,799470,799665,810476,818433,833469,1004979,1010203,1023392,1045098,1047570,1047575,1047576,1049484,1049492,1049609,1050908,1059592,1063510,1064284,1064569,1065894,1067005,1067006,1067007,1069186,1069358,1072956,1072957,1087312,1091640,1093751,1100891,1107232,1116313,1116782,1118639,1130793,1131469,1133625,1136245,1145855,1145856,1146930,1147846,1148242,1148243,1148504,1155517,1158732,1169722,1170354,1174377,1179337,1179356,1199981,1206521,1208329,1209995,1212772,1214018,1220366,1220916,1221845,1223265,1226430,1227371,1232757,1234781,1235266,1235267,1235622,1237925,1238537,1239003,1240333,1240531,1240775,1245464,1263862,1269201,1269202,1271296,1272638,1273871,1274309,1277216,1277217,1278881,1292552,1315344,1315345),
                     str_replace(a, "car lt", "tudor car l"), a),
              a = ifelse(ID %in% c(630338,751198,757198,776643,814931,1083212,1133188,1147741,1206647,1225195,1277602,1294533),
                     str_replace(a, "griep lmo", "oude griep lm"), a),
              a = ifelse(ID == 755730,
                     str_replace(a, "garcia lm", "monje garcia l"), a),
              a = ifelse(ID == 690133,
                     str_replace(a, "segura m", "segura lepe mp"), a),
              a = ifelse(ID == 791334,
                     str_replace(a, "martinez ar", "rodriguez martinez a"), a),
              a = ifelse(ID %in% c(701990,717069,760357,784991,810602,833517,833518,833519,833521,833522,833523,836293,886203,886204,886206,976725,976728,981464,1001367,1084524,1093990,1099618,1118368,1131286,1145000,1155468,1155706,1155765,1158690,1167814,1169601,1174569,1174877,1175531,1177757,1179842,1181078,1181618,1182124,1189849,1189886,1193410,1195147,1196231,1197088,1202844,1206639,1211285,1211525,1217726,1224112,1226889,1227459,1234245,1235770,1245688,1254418,1258689,1267291,1278804, 1184684),
                     str_replace(a, "cucunubá", "cucunuba perez"), a),
                            a = ifelse(ID %in% c(701990,717069,760357,784991,810602,833517,833518,833519,833521,833522,833523,836293,886203,886204,886206,976725,976728,981464,1001367,1084524,1093990,1099618,1118368,1131286,1145000,1155468,1155706,1155765,1158690,1167814,1169601,1174569,1174877,1175531,1177757,1179842,1181078,1181618,1182124,1189849,1189886,1193410,1195147,1196231,1197088,1202844,1206639,1211285,1211525,1217726,1224112,1226889,1227459,1234245,1235770,1245688,1254418,1258689,1267291,1278804, 1196618),
                     str_replace(a, "cucunuba", "cucunuba perez"), a),
               a = ifelse(ID %in% c(814816,820061,1069150,1132846,1175601,1204049,1208342,1218539,1234245,1245688,1267291),
                     str_replace(a, "dixon ma", "dixon-zegeye mas"), a),
              a = ifelse(ID %in% c(890313,890327,890403,897969,959298,1118635,1187725,1193410,1202844,1240018),
                     str_replace(a, "nascimento ff", "ferreira do nascimento"), a),
              a =  ifelse(ID %in% c(1181078, 1197234,890403,897969,959298,1118635,1187725,1193410,1202844,1240018),
                     str_replace(a, "mesa do", "olivera mesa d"), a),
              a =   ifelse(ID == 1174132,
                     str_replace(a, "yamamoto hq", "quezada yamamoto h"), a),
              a = ifelse(ID == 1165644,
                     str_replace(a, "delisle tg", "georgious-delisle t"), a),
              a = ifelse(ID %in% c(1060823,1060825,1060826,1060827,1060828,1060829,1060830,1060832,1228068,1256963),
                     str_replace(a, "van kn", "nguyen vk"), a),
              a = ifelse(ID %in% c(1154504,1154550,1154551),
                     str_replace(a, "y h", "han y"), a),
              a = ifelse(ID == 1167206,
                     str_replace(a, "bina r", "ram b"), a),
              a = ifelse(ID %in% c(1194212, 1274326),
                     str_replace(a, "daniels bc", "cracknell daniels bn"), a),
              a = ifelse(ID == 1286578,
                     str_replace(a, "frank k", "kelly f"), a),
              a = ifelse(ID == 1306415,
                     str_replace(a, "d d", "dajnak d"), a),
              a = ifelse(ID == 1065862,
                     str_replace(a, "tuan v", "vu tv"), a),
              a = ifelse(ID%in% c(1135943, 1196535),
                     str_replace(a, "tuan vv", "vu tv"), a),
              a = ifelse(ID%in% c(1226593, 1258749),
                     str_replace(a, "wright hr", "rapp wright hl"), a),
              a = ifelse(ID%in% c(1153587, 1153588, 1165212, 1162463, 1167577,
                                  1183803, 1201967, 1204151,1204158,1219913,
                                  1252154,1262982),
                     str_replace(a, "candido", "da silva candido"), a),
              a = ifelse(ID %in% c(1262980,1262982),
                     str_replace(a, "cândido", "da silva candido"), a),
              a = ifelse(ID %in% c(656481, 692257, 705870),
                     str_replace(a, "rosenblatt", "navarro rosenblatt"), a),
              a = ifelse(ID %in% c(1267739, 1267740, 1267741, 1267742,
                                   1267743, 1267744, 1267745, 1267750,
                                   1248644),
                     str_replace(a, "shaweno d", "adewo ds"), a),
              a = ifelse(ID %in% c(1170959, 1170960, 1170961, 1170976,
                                   1170979, 1170981, 1261097, 1262737),
                         str_replace(a, "puvanachandra", "attwood"), a),
              a = ifelse(ID %in% c(1170701, 1174924),
                         str_replace(a, " de jager ca", "loots ca"), a),
              a = ifelse(ID %in% c(787462, 821773, 1008728, 1077350, 1205747,
                                   1205806, 1281405),
                         str_replace(a, " rajani nb", "n weth"), a),
              Authors.OR.Authors.Contributors = a)



# Checking the impact of the update
dat <- dat %>%
  mutate(contained = str_detect(Authors.OR.Authors.Contributors, paste("\\b", last_name, "\\b", sep="")))

dat %>% 
  group_by(contained) %>%
  summarise(n=n())
```


Identify all entries where individual position is missing and working group is present. 

Hypothesis: individual position is missing in many cases due to working group present. -> This has a significant impact on results.

```{r}
# set up dataframe to identify where working groups are present
working_groups_df <- data.frame(WorkingGroupName = character(0), ID = numeric(0))

# identify all authors/author groups listed in Authors.OR.Authors.Contributors
dat_sub <- str_split(dat$Authors.OR.Authors.Contributors,",")

# remove spaces at beginning
dat_sub <- data.frame(unlist(lapply(dat_sub, function(vec) trimws(vec))))
names(dat_sub) <- c("full_name")
dat_vector_dict <- dat_sub
dat_vector_dict$full_name <- trimws(dat_vector_dict$full_name)

# remove point and () (and values inside ())
dat_vector_dict$full_name <- gsub("\\([^\\)]+\\)", "", dat_vector_dict$full_name)
dat_vector_dict$full_name <- gsub("\\.", "", dat_vector_dict$full_name)

# Split the 'full_name' column by space into new columns
df_split <- dat_vector_dict %>%
  separate(full_name, into = paste0("name_element_", 1:300), sep = " ",  fill = "right")

df_split <- df_split %>%
  select(where(~any(!is.na(.))))

# for later identificaion of full working group names
df_split$identity <- dat_vector_dict$full_name

# might be irrelevant  
df_split <- df_split %>%
  select(where(~any(!is.na(.))))%>%
  mutate_all(tolower)%>%
  distinct()

# Words to exclude that hint at consortia/working groups etc
excluded_words <- c("modelling","opthalmologists", "program", "etiology", "group", "education", "consortium","committee",
                    "network","collaborative", 
                    "genetics", "collaboration", "hypertension", "investigators","diseases", "database","community","analysis",
                    "nutrition", "team","gomide", "epidemiology", "expert", "society", "investigators", "accademia", "collaborators", 
                    "study", "academia", "conference","project","table","laboratory","organization","organisation", "who",
                    "federation")

# create dataframe that only includes working groups
working_groups <- df_split %>%
  filter_all(any_vars(str_detect(., paste(excluded_words, collapse = "|"))))

# save as vector
working_groups_vec <- unique(working_groups$identity)

# remove space at beginning of working group name
working_groups_vec <- trimws(working_groups_vec)

```


Search for working group names in Authors.Or.Authors.Contributors column.

```{r}

# Empty df to collect info on WorkingGroupName and ID (from dat)
working_groups_df <- data.frame(WorkingGroupName = character(0), ID = numeric(0))

cleaned_author <- dat$Authors.OR.Authors.Contributors
cleaned_author <- gsub("\\([^\\)]+\\)", "", cleaned_author)
cleaned_author <- gsub("\\.", "", cleaned_author)

# Loop through each search word
for (i in seq_along(working_groups_vec)) {
  # Use grepl to check if the word is present in the specified column
  mask <- grepl(working_groups_vec[i], cleaned_author, fixed = TRUE)
  
  # If the word is found, retrieve the corresponding ID from column 1
    if (any(mask)) {
    corresponding_id <- dat[mask, "ID"][1]
    
    # Add the result to the results data frame
    working_groups_df <- rbind(working_groups_df, data.frame(WorkingGroupName = working_groups_vec[i], ID = corresponding_id))
  }
}
```

Identify correct initials. Names cannot be split based on spaces due to double last names. 



```{r}
# remove working_groups rows from df_split
split_df_filtered <- anti_join(df_split, working_groups)

```

```{r}
# remove all columns where all empty
split_df_filtered <- split_df_filtered %>%
  select(where(~any(!is.na(.))))

# search for all that begin with van or von/de/da (double names/longer names)
split_df_updated <- split_df_filtered %>%
  rowwise() %>%
  mutate(von_van = str_detect(paste(c_across(starts_with("name_element_")), collapse = " "), "\\b(van|von|de|da|do|dos|la|del|das|al|el|di|le|la|lo)\\b")) %>%
  mutate(group_var = cumsum(lag(!von_van, default = TRUE) & von_van)) %>%
  group_by(group_var) %>%
  mutate(
    last_name_estim = ifelse(von_van & !is.na(name_element_6), 
                             paste(name_element_1, 
                                   name_element_2, 
                                   name_element_3, 
                                   name_element_4, 
                                   name_element_5, sep = " "),
                             
                             ifelse(von_van & !is.na(name_element_5), 
                             paste(name_element_1, 
                                   name_element_2, 
                                   name_element_3, 
                                   name_element_4, sep = " "),
                             
                             ifelse(von_van & !is.na(name_element_4), 
                             paste(name_element_1, 
                                   name_element_2, 
                                   name_element_3, sep = " "),
                             
                             ifelse(von_van & !is.na(name_element_3), 
                             paste(name_element_1, 
                                   name_element_2, sep = " "), NA_character_)))),
    first_name_estim = if_else(von_van & !is.na(last_name_estim),
                               if_else(!is.na(name_element_6), name_element_6,
                               if_else(!is.na(name_element_5), name_element_5,
                               if_else(!is.na(name_element_4), name_element_4,
                                       if_else(!is.na(name_element_3), name_element_3,
                                               if_else(!is.na(name_element_2), name_element_2,
                                                       if_else(!is.na(name_element_1), name_element_1, NA_character_)))))), NA_character_)
  ) %>%
  ungroup()  # Ungroup to remove grouping


von_van_df <- split_df_updated %>%
  filter(!is.na(first_name_estim) & !is.na(last_name_estim))

# remove rows from split_df_updated
split_df_updated <- anti_join(split_df_updated, von_van_df)
```


Identify where only last name. 

```{r}
split_df_updated <- split_df_updated %>%
  select(where(~any(!is.na(.))))

split_df_updated <- split_df_updated %>%
  rowwise() %>%
  mutate(
    last_name_estim = if_else(nchar(name_element_1 > 1) & is.na(name_element_2),
                              name_element_1,
                              NA_character_)
  )

only_last <- split_df_updated %>%
  filter(!is.na(last_name_estim))

only_last$first_name_estim <- NA
split_df_updated <- anti_join(split_df_updated, only_last)


```

Identify is the first name and last name are in the right order. 

```{r}
split_df_updated <- split_df_updated %>%
  select(where(~any(!is.na(.))))

split_df_updated <- split_df_updated %>%
  rowwise() %>%
  mutate(
    last_name_estim = if_else(!is.na(name_element_1) & !is.na(name_element_2) & is.na(name_element_3),
                              if_else(nchar(name_element_1) >= nchar(name_element_2), name_element_1, name_element_2),
                              NA_character_),
    first_name_estim = if_else(!is.na(name_element_1) & !is.na(name_element_2) & is.na(name_element_3),
                               if_else(nchar(name_element_1) >= nchar(name_element_2), name_element_2, name_element_1),
                               NA_character_)
  )


easy_names <- split_df_updated %>%
  filter(!is.na(first_name_estim) & !is.na(last_name_estim))

split_df_updated <- anti_join(split_df_updated, easy_names)

```

```{r}

# search for all that begin with van or von/de/da (double names/longer names)
split_df_updated <- split_df_updated %>%
  mutate(
    last_name_estim = ifelse(!is.na(name_element_5), 
                             paste(name_element_1, name_element_2, name_element_3, name_element_4, sep = " "),
                             ifelse(!is.na(name_element_4), 
                                    paste(name_element_1, name_element_2, name_element_3, sep = " "),
                                    ifelse(!is.na(name_element_3), 
                                           paste(name_element_1, name_element_2, sep = " "), 
                                           NA_character_)
                             )
    ),
    first_name_estim = ifelse(!is.na(last_name_estim),
                              ifelse(!is.na(name_element_5), name_element_5,
                                     ifelse(!is.na(name_element_4), name_element_4,
                                            ifelse(!is.na(name_element_3), name_element_3,
                                                   ifelse(!is.na(name_element_2), name_element_2,
                                                          ifelse(!is.na(name_element_1), name_element_1, NA_character_)
                                                   )
                                            )
                                     )
                              ), NA_character_
    )
  )


remaining_names <- split_df_updated %>%
  filter(!is.na(first_name_estim) & !is.na(last_name_estim))

# remove rows from split_df_updated
split_df_updated <- anti_join(split_df_updated, remaining_names)
# split_df_updated should be of length 0 if all names have been first/last named through algorithm
```

Merge all the sub dataframes: easy names, only_last, von_van_df, remaining names

df_temp is the final dataset that should be used for subsequent comparison of initials with names in dat

```{r}
df_temp <- rbind(easy_names[,c("identity","last_name_estim","first_name_estim")], 
                 only_last[,c("identity","last_name_estim","first_name_estim")], 
                 von_van_df[,c("identity","last_name_estim","first_name_estim")], 
                 remaining_names[,c("identity","last_name_estim","first_name_estim")])

df_temp <- unique(df_temp)
```


```{r}
# Check surname similarity
# requires stringdist package
# similar_surname, intended as a flag
# doesn't account for cases where initial is first
similar_surname_in_authors <- function(all_authors, last_name,
                                       author_df,  threshold=0.85){
  # Does not work for cases where the initial is first
  # Get a list of authors
  list_of_authors <- sapply(unlist(strsplit(all_authors, ",")), str_trim)

  distance <- 0
  matching_author <- ""
  for (author in list_of_authors){

    last_name_estim <- unlist(author_df[(author_df$identity == author), "last_name_estim"])[1]

    if(!is.na(last_name_estim)){
    temp_distance <- stringdist::stringsim(last_name_estim, last_name,
                                           method="cosine")

    if (temp_distance > threshold & temp_distance > distance){
      distance <- temp_distance
      matching_author <- paste(author, round(distance,2), sep=";")
      }
    }
  }

  return (matching_author)
}

# 
# cosine_author_names <- sapply(1:NROW(dat),
#                     function(i) similar_surname_in_authors(dat$all_authors[i],
#                                                            dat$last_name[i], 
#                                                            df_temp))
dat["cosine_last_name_author_dist"] <- ""

pb = txtProgressBar(min = 0, max = NROW(dat), initial = 0) 

for (i in 1:NROW(dat)){
  dat[i, "cosine_last_name_author_dist"] <- similar_surname_in_authors(dat$Authors.OR.Authors.Contributors[i],
                                                                       dat$last_name[i], 
                                                                       df_temp)
  
  setTxtProgressBar(pb, i)

}

close(pb)

dat <- dat %>%
  mutate(cosine_last_name_flag = (cosine_last_name_author_dist!=""))

dat %>%
  group_by(contained, cosine_last_name_flag) %>% 
  summarise(n=n())
```

Manually checking and filtering out the bad matches
```{r}
dat <-  dat %>% mutate(UID = paste(ID, User.s.Proprietary.ID, sep="_"))

dat %>% filter(cosine_last_name_flag == TRUE & contained == FALSE) %>%
  select(UID, ID, Name, initials, last_name,  cosine_last_name_author_dist) %>% 
  writexl::write_xlsx("../manual_checking/cosine_matches_not_contained.xlsx")

# 26 matches were incorrect
# Use new uid since there may be other correct matches with the same ID 
ids_to_exclude <- c("1167577_ddasilva",
                    "1266695_sanand",
                    "1009316_clill",
                    "752735_smacmaho",
                    "656481_dnavarro",
                    "692257_dnavarro",
                    "705870_dnavarro",
                    "1213008_cfraser",
                    "1217243_cfraser",
                    "1217778_cfraser",
                    "1250443_cfraser",
                    "792119_jaw32",
                    "811876_jaw32",
                    "978295_jaw32",
                    "1021735_jaw32",
                    "1054095_jaw32",
                    "1064216_jaw32",
                    "1167150_qchan30",
                    "1148242_srawaf",
                    "1148243_srawaf",
                    "1155569_ar3513",
                    "1044222_ssaxena",
                    "1179337_amajeed",
                    "780543_mrj30",
                    "786350_mrj30",
                    "810740_mrj30")


dat <- dat %>% mutate(cosine_last_name_author_dist = ifelse(UID %in% ids_to_exclude,
                                                     "", cosine_last_name_author_dist))

dat <- dat %>%
  mutate(cosine_last_name_flag = (cosine_last_name_author_dist!=""))

dat %>%
  group_by(contained, cosine_last_name_flag) %>% 
  summarise(n=n())
```

```{r}
get_individual_position <- function(all_authors,
                                    last_name,
                                    cosine_name_match,
                                    author_df){
  # Does not work for cases where the initial is first
  # Get a list of authors
  list_of_authors <- sapply(unlist(strsplit(all_authors, ",")), str_trim)

  for (i in 1:length(list_of_authors)){
    author <- list_of_authors[[i]]

    if (is.na(author)) next
    if (author == "") next

    if (cosine_name_match == author){
      return (i)
    }
    
    last_name_estim <- unlist(author_df[(author_df$identity == author), "last_name_estim"])[1]
    
    if (!is.na(last_name_estim)){
      if(last_name_estim == last_name){
        return (i)
      }
    }
  }

  return (NA)
}

dat <- dat %>% mutate(cosine_name_match = str_split(cosine_last_name_author_dist, ";", simplify = TRUE)[,1])


pb = txtProgressBar(min = 0, max = NROW(dat), initial = 0) 

for (i in 1:NROW(dat)){
  dat[i, "individual_position"] <- get_individual_position(dat$Authors.OR.Authors.Contributors[i],
                                                           dat$last_name[i],
                                                           dat$cosine_name_match[i],
                                                           df_temp)
  
  setTxtProgressBar(pb, i)
}

close(pb)
```

```{r}
dat <- dat %>% mutate(working_group_flag = (ID %in% working_groups_df$ID))
```


```{r}
# 4 TRUE contained and FALSE cosine_last_name matches are due to initials with 3 letters -
# the mataches were manually checked
dat %>%
  group_by(contained, cosine_last_name_flag, working_group_flag) %>%
  summarise(n=n())
```

```{r}
dat <- dat %>% mutate(author_position = ifelse(!is.na(individual_position), "middle", author_position),
                      author_position = ifelse(individual_position==1, "first", author_position),
                      author_position = ifelse(individual_position==N_authors, "last", author_position),
               author_position = ifelse(is.na(author_position) & working_group_flag==TRUE, "working group", author_position))

# Imperial COVID-19 Response team
# Not sure if this list is exhaustive, but based on reports I could find attached to
# an unnamed author in the author list with an NA author position
C19RT_Reports <- c(1140112, 1140115, 1140116, 1142831, 114498, 1146729, 1148217, 1153716,
1155733, 1156505, 1158552, 1181066, 1183624, 1183639, 1184094, 1185989,
1186104, 1186107, 1187728, 1190142, 1204792, 1228788, 1238348, 1238555,
1242093, 1273847, 1143357)

dat <- dat %>% mutate(author_position = ifelse(is.na(author_position) & ID %in% C19RT_Reports,
                                               "working group", author_position))

```

```{r}
dat %>% filter(is.na(author_position)) %>%
  group_by(contained) %>%
  summarise(n=n())

dat %>% filter(is.na(author_position)) %>%
  select(ID, Name, initials, last_name, Authors.OR.Authors.Contributors, contained, DOI) %>%
  writexl::write_xlsx("../manual_checking/na_individual_positions.xlsx")
```
Final results:

```{r}
dat_complete <-  dat_complete %>%
  mutate(UID = paste(ID, User.s.Proprietary.ID, sep="_"))

# Assuming UID is unique, there are duplicates in the dataset:
dat_complete %>%
  group_by(UID) %>% 
  summarise(n=n()) %>%
  arrange(desc(n)) %>% 
  filter(n>1)

# => 24 extra rows since there will be two rows for each of the 12 rows below
dat %>% 
  group_by(UID) %>%
  summarise(n=n()) %>%
  arrange(desc(n)) %>%
  filter(n>1)

dat_complete <- dat_complete %>%
  distinct(UID, .keep_all = TRUE) 

dat <- dat %>%
  distinct(UID, .keep_all = TRUE)

```

```{r}
dat %>% 
  group_by(author_position) %>% 
  summarise(n=n())

# saving incase we need to check any of the estimated author positions
dat %>% write.csv("../manual_checking/author_estimation_dataset.csv",
                  row.names = FALSE)
```

```{r}
dat_complete <- dat_complete %>% 
  left_join(dat %>% select(UID, individual_position, author_position), by="UID", suffix = c("", "_estimated"))

dat_complete <- dat_complete %>%
  mutate(author_position = ifelse(is.na(author_position), author_position_estimated, author_position),
         individual_position = ifelse(is.na(individual_position), individual_position_estimated, individual_position))
```

```{r}
dat_complete%>% 
  group_by(author_position) %>% 
  summarise(n=n())

dat_complete %>%
  write.csv("../interim/clean_data_job_title_author_pos.csv", row.names = FALSE)
```
